Fast Automatic Bayesian Cubature Using Lattice Sampling

### 2019-07-29 BayesianCubaturePaper2018 - Rev1c.tex
single column edits

Furthermore, for a Gaussian process, all vectors of linear functionals of $f$ have a multivariate Gaussian distribution. For any deterministic sampling scheme with distinct nodes, $\{\vx_i\}_{i=1}^n$, and defining  $\vf  := \left( f(\vx_i)\right)_{i=1}^n$ as the multivariate Gaussian vector of function values, it follows from the definition of a Gaussian process that 
\begin{subequations} \label{eqn:fGaussDist}
\begin{align}
\vf  & \sim \calN(m \vone, s^2 \mCtheta), \\
\nonumber & \qquad \qquad \text{where $\vone$ is a vector of all ones,}\\
\mu & \sim \calN(m, s^2 c_{0\vtheta}), 
\\
\text{where }
c_{0\vtheta} &:= \int_{[0,1]^{d}\times [0,1]^{d}} C_\vtheta(\vt,\vx) \, \dif{\vt} \, \dif{\vx}, \text{ and}\\
\cov(\vf, \mu) &= \left(  \int_{[0,1]^d} C_\vtheta(\vt,\vx_i) \, \D \vt \right)_{i=1}^n  =: \vc_\vtheta.
\end{align}
\end{subequations}
Here, $c_{0\vtheta}$ and $\vc_\vtheta$ depend explicitly on $\vtheta$.  We assume that $C_\vtheta$ is simple enough that the integrals in these definitions can be computed analytically.  We need the following lemma pertaining to a conditional Gaussian distribution to derive the distribution of the posterior error of our cubature.

\begin{lemma} \cite[(A.6), (A.11--13)]{RasWil06a} \label{thrm:condDist} If $\vY = (\vY_1, \vY_2)^T \sim \calN (\vm,\mSigma)$, where $\vY_1$ and $\vY_2$ are random vectors of arbitrary length, and 
	\begin{gather*}
	\vm = \begin{pmatrix} \vm_1 \\ \vm_2 \end{pmatrix} = \begin{pmatrix} \Ex(\vY_1) \\ \Ex(\vY_2) \end{pmatrix}, \\
	\mSigma = \begin{pmatrix}
	\mSigma_{11} & \mSigma_{21}^T \\ 	\mSigma_{21} & \mSigma_{22}
	\end{pmatrix} =
	\begin{pmatrix}
	\var(\vY_{1}) & \cov(\vY_{1}, \vY_2) \\ 	\cov(\vY_2,\vY_{1}) & \var(\vY_{2})
	\end{pmatrix} 
	\end{gather*}
	then 
	\begin{align*}
	\vY_1 \vert \vY_2 \; \sim \; \calN \bigl(\vm_1 + \mSigma_{21}^T \mSigma_{22}^{-1}(\vY_2 - \vm_2),  \; \mSigma_{11} - \mSigma_{21}^T \mSigma_{22}^{-1} \mSigma_{21} \bigr).
	\end{align*}
Moreover, the inverse of the matrix $\mSigma$ may be partitioned as
\begin{gather*}
\mSigma^{-1} = \begin{pmatrix} \mA_{11} & \mA_{21}^T \\ \mA_{21} & \mA_{22} \end{pmatrix}, \\
\mA_{11} = (\mSigma_{11} - \mSigma_{12} \mSigma_{22}^{-1} \mSigma_{21})^{-1}, \qquad 
\mA_{21} = -  \mSigma_{22}^{-1} \mSigma_{21} \mA_{11}, \\ 
\mA_{22} = \mSigma_{22}^{-1} + \mSigma_{22}^{-1} \mSigma_{21} \mA_{11} \mSigma_{21}^T \mSigma_{22}^{-1}.
\end{gather*}

@@

\begin{theorem} \label{thm:param} There are at least three approaches to estimating or integrating out the hyperparameters defining the Gaussian process from which the integrand is drawn: empirical Bayes, full Bayes, and generalized cross-\linebreak[4]validation.  Under these three approaches, we have the following:
\begin{align}
    \label{eqn_m_MLE}
m_\MLE &= \frac{\vone^T \mCInv_\vtheta \vy }{ \vone^T \mCInv_\vtheta \vone}, \qquad
m_{\textup{GCV}} = \frac{\vone^T \mC_\vtheta^{-2} \vy}{\vone^T \mC_\vtheta^{-2} \vone}, \\
\label{eqn_s2_MLE}
s^2_{\MLE} 
&= 
\frac{1}{n}
\vy^T 
\left[ \mCInv_\vtheta - 
\frac{ \mCInv_\vtheta \vone \vone^T \mCInv_\vtheta }{\vone^T\mCInv_\vtheta \vone}
\right] \vy, \\
\nonumber
\hsigma_{\full}^2 
& = \frac{1}{n-1}
\vy^T\left[ \mC_\vtheta^{-1} 
- \frac{ \mC_\vtheta^{-1} \vone\vone^T \mC_\vtheta^{-1}}{\vone^T \mC_\vtheta^{-1} \vone}  \right]\vy
\\ 
\label{eqn:sigma2_full}
& \times  \left[\frac{(1 - \vc_{\vtheta}^T \mC_\vtheta^{-1} \vone)^2}{\vone^T \mC_\vtheta^{-1} \vone} + (c_{0\vtheta}  -\vc_{\vtheta} ^T \mC_\vtheta^{-1} \vc_{\vtheta}) \right], \\
\nonumber
 s^2_{\textup{GCV}} & = \vy^T \left[\mC_\vtheta^{-2} - \frac{\mC_\vtheta^{-2} \vone \vone^T \mC_\vtheta^{-2}}{\vone^T \mC_\vtheta^{-2} \vone}  \right] \vy  \left[ \trace(\mC_\vtheta^{-1}) \right]^{-1}, \\
\label{eqn:thetaMLE}
\vtheta_\MLE
&= \argmin_{\vtheta} \biggl \{
\log\left(\vy^T 
\left[ \mC_\vtheta^{-1} - 
\frac{ \mCInv_\vtheta \vone \vone^T \mCInv_\vtheta }{\vone^T\mCInv_\vtheta \vone}
\right] \vy 
\right)  
 +  \frac{1}{n} \log(\det(\mC_\vtheta))
\biggr \}, \\
\label{vthetaGCV}
\vtheta_{\GCV} &= \argmin_\vtheta \biggl\{\log \left(  \vy^T \left[\mC^{-2}_\vtheta - \frac{\mC^{-2}_\vtheta \vone \vone^T \mC^{-2}_\vtheta}{\vone^T \mC^{-2}_\vtheta \vone}  \right] \vy \right)  
 - \log \left ( \trace(\mC^{-2}_\vtheta) \right ) \biggr\}, \\
\label{eqn:cubMLE}
\hmu_\MLE  &= \hmu_\full =
\left(
\frac{ (1 - \vone^T  \mCInv_\vtheta\vc_{\vtheta} )  \vone }{ \vone^T \mCInv_\vtheta \vone}   +  \vc_{\vtheta} 
\right)^T  \mCInv_\vtheta \vy, \\
\label{eqn:muCV}
\hmu_{\GCV}
& = \left(\frac{(1 - \vone^T  \mC_\vtheta^{-1}\vc_{\vtheta}) \mC_\vtheta^{-1} \vone}{\vone^T \mC_\vtheta^{-2} \vone} + \vc_{\vtheta} \right)^T \mC_\vtheta^{-1} \vy.
\intertext{The credible intervals widths, $\err_{\textup{CI}}$, are given by}
\label{eqn:err_MLEGCV}
\err_{\mathsf{x}} & = 2.58 s_{\mathsf{x}} \sqrt{c_{0\vtheta} - \vc_{\vtheta}^T\mC_\vtheta^{-1}\vc_{\vtheta} }, \qquad \mathsf{x} \in \{\MLE, \GCV\},  \\ 
\err_{\textup{full}} 
& = t_{n-1,0.995} \hsigma_{\textup{full}} > \err_\MLE. \label{FJH:eq:errFull}
\end{align}
The resulting credible intervals are then
\begin{align}
\label{eqn_prob_CI}
\mathbb{P}_f \left[
|\mu-\hmu_{\mathsf{x}}| \leq \err_{\mathsf{x}} \right]  = 99\%, \qquad \mathsf{x} \in \{\MLE, \full, \GCV\}.
\end{align}
Here $t_{n-1,0.995}$ denotes the $99.5$ percentile of a standard Student's $t$-distribution with $n-1$ degrees of freedom.  In the formulas above, $\vtheta$ is assumed to take on the values $\vtheta_{\MLE}$ or $\vtheta_{\GCV}$ as appropriate.
\end{theorem}

@@

Let $\mA = \mC^{-1}_\vtheta$, let $\vzeta = \mA (\vy - m \vone)$, and partition $\mC_\vtheta$, $\mA$, and $\vzeta$ as
\begin{gather*}
\mC_\vtheta = \begin{pmatrix} c_{ii}  & \vC_{-i,i}^T \\  \vC_{-i,i} & \mC_{-i,-i}\end{pmatrix}, \qquad
\mA = \begin{pmatrix} a_{ii}  & \vA_{-i,i}^T \\  \vA_{-i,i} & \mA_{-i,-i}\end{pmatrix}, \\ \vzeta = \begin{pmatrix} \zeta_i   \\  \vzeta_{-i} \end{pmatrix},
\end{gather*}
where the subscript $i$ denotes the $i^{\text{th}}$ row or column, and the subscript $-i$ denotes all rows or columns except the $i^{\text{th}}$. Following this notation, Lemma \ref{thrm:condDist} implies that 
\begin{align*}
\mathring{y}_i & = m + \vC^T_{-i,i} \mC_{-i,-i}^{-1} (\vy_{-i} -m \vone)  \\
\zeta_i  & = a_{ii}(y_i - m) + \vA_{-i,i}^T(\vy_{-i} - m \vone) \\
& = a_{ii}[(y_i - m) - \vC^T_{-i,i} \mC_{-i,-i}^{-1} (\vy_{-i} -m \vone)] \\
& = a_{ii}(y_i - \mathring{y}_i).
\end{align*}
Thus, \eqref{FJH:eq:CVA} may be re-written as 
\begin{align*} %\label{FJH:eq:CVB}
\textup{CV} = \sum_{i=1}^n \left(\frac{\zeta_i}{a_{ii}} \right)^2, \qquad \vzeta = \mC^{-1}_\vtheta(\vy - m \vone).
\end{align*}
The \emph{generalized cross-validation} criterion (GCV) replaces the $i^{\text{th}}$ diagonal element of $\mA$ in the denominator by the average diagonal element of $\mA$ \cite{CraWah79a,GolHeaWah79a,Wah90}:
\begin{align*} 
\textup{GCV} &
= \frac{\sum_{i=1}^n\zeta_i^2}{\left(\frac 1n \sum_{i=1}^n a_{ii} \right)^2} \\
& = \frac{(\vy - m\vone)^T \mC^{-2}_\vtheta (\vy - m \vone)}{\left(\frac 1n \trace(\mC_\vtheta^{-1}) \right)^2}.
\end{align*}

@@

The generic automatic Bayesian cubature algorithm described in the previous section requires $\Order\bigl(n \$(f) + \linebreak[4] N_{\opt} [n^2 \$(C_\vtheta) + n^3]\bigr)$ operations to compute the cubature. Now we explain how to speed up the calculations. A key is to choose covariance kernels that match the nodes, $\{\vx_i\}_{i=1}^n$, so that the vector-matrix operations required by Bayesian cubature can be accomplished using fast Bayesian transforms at a computational cost of $\Order\bigl(n \$(f) + N_{\opt} [n \$(C_\vtheta)  + n \log(n)] \bigr)$.

@@

We have implemented the fast adaptive Bayesian cubature algorithm in MATLAB as part of the Guaranteed Adaptive Integration Library (GAIL) \cite{ChoEtal17b} as \linebreak[4]  \code{cubBayesLattice\_g}. This algorithm uses the covariance kernel defined in \eqref{eqn:ourkernel} with  $r=1$ and $2$, and the periodizing variable transforms in  \secref{period_var_tx}.  The rank-1 lattice node generator is taken from \cite{Nuy17a} \linebreak[4] (\code{exod2\_base2\_m20}).

@@

We have developed a fast, automatic Bayesian cubature that estimates a multidimensional definite integral within a user defined error tolerance.  The stopping criteria arise from assuming the integrand to be an instance of a Gaussian process. There are three approaches:  empirical Bayes, full Bayes, and generalized cross-validation.  The computational cost of the automatic Bayesian cubature can be dramatically reduced if the covariance kernel matches the nodes.  One such match in practice is rank-1 lattice nodes and shift-\linebreak[4]invariant kernels.  The matrix-vector multiplications can be accomplished using the fast Fourier Transform.  The performance of our automatic Bayesian cubature is illustrated using three integration problems.

>>>>

Furthermore, for a Gaussian process, all vectors of linear functionals of $f$ have a multivariate Gaussian distribution. For any deterministic sampling scheme with distinct nodes, $\{\vx_i\}_{i=1}^n$, and defining  $\vf  := \left( f(\vx_i)\right)_{i=1}^n$ as the multivariate Gaussian vector of function values, it follows from the definition of a Gaussian process that 
\begin{subequations} \label{eqn:fGaussDist}
\begin{align}
\vf  & \sim \calN(m \vone, s^2 \mCtheta),  \qquad \text{where $\vone$ is a vector of all ones,}\\
\mu & \sim \calN(m, s^2 c_{0\vtheta}), 
\\
\text{where }
c_{0\vtheta} &:= \int_{[0,1]^{d}\times [0,1]^{d}} C_\vtheta(\vt,\vx) \, \dif{\vt} \, \dif{\vx}, \text{ and}\\
\cov(\vf, \mu) &= \left(  \int_{[0,1]^d} C_\vtheta(\vt,\vx_i) \, \D \vt \right)_{i=1}^n  =: \vc_\vtheta.
\end{align}
\end{subequations}
Here, $c_{0\vtheta}$ and $\vc_\vtheta$ depend explicitly on $\vtheta$.  We assume that $C_\vtheta$ is simple enough that the integrals in these definitions can be computed analytically.  We need the following lemma pertaining to a conditional Gaussian distribution to derive the distribution of the posterior error of our cubature.

\begin{lemma} \cite[(A.6), (A.11--13)]{RasWil06a} \label{thrm:condDist} If $\vY = (\vY_1, \vY_2)^T \sim \calN (\vm,\mSigma)$, where $\vY_1$ and $\vY_2$ are random vectors of arbitrary length, and 
	\begin{gather*}
	\vm = \begin{pmatrix} \vm_1 \\ \vm_2 \end{pmatrix} = \begin{pmatrix} \Ex(\vY_1) \\ \Ex(\vY_2) \end{pmatrix}, \\
	\mSigma = \begin{pmatrix}
	\mSigma_{11} & \mSigma_{21}^T \\ 	\mSigma_{21} & \mSigma_{22}
	\end{pmatrix} =
	\begin{pmatrix}
	\var(\vY_{1}) & \cov(\vY_{1}, \vY_2) \\ 	\cov(\vY_2,\vY_{1}) & \var(\vY_{2}),
	\end{pmatrix} 
	\end{gather*}
	then 
	\begin{align*}
	\vY_1 \vert \vY_2 \; \sim \; \calN \bigl(\vm_1 + \mSigma_{21}^T \mSigma_{22}^{-1}(\vY_2 - \vm_2),  \; \mSigma_{11} - \mSigma_{21}^T \mSigma_{22}^{-1} \mSigma_{21} \bigr).
	\end{align*}
Moreover, the inverse of the matrix $\mSigma$ may be partitioned as
\begin{gather*}
\mSigma^{-1} = \begin{pmatrix} \mA_{11} & \mA_{21}^T \\ \mA_{21} & \mA_{22} \end{pmatrix}, \\
\mA_{11} = (\mSigma_{11} - \mSigma_{12} \mSigma_{22}^{-1} \mSigma_{21})^{-1}, \qquad 
\mA_{21} = -  \mSigma_{22}^{-1} \mSigma_{21} \mA_{11}, \\ 
\mA_{22} = \mSigma_{22}^{-1} + \mSigma_{22}^{-1} \mSigma_{21} \mA_{11} \mSigma_{21}^T \mSigma_{22}^{-1}.
\end{gather*}

@@

\begin{theorem} \label{thm:param} There are at least three approaches to estimating or integrating out the hyperparameters defining the Gaussian process from which the integrand is drawn: empirical Bayes, full Bayes, and generalized cross-validation.  Under these three approaches, we have the following:
\begin{align}
    \label{eqn_m_MLE}
m_\MLE &= \frac{\vone^T \mCInv_\vtheta \vy }{ \vone^T \mCInv_\vtheta \vone}, \qquad
m_{\textup{GCV}} = \frac{\vone^T \mC_\vtheta^{-2} \vy}{\vone^T \mC_\vtheta^{-2} \vone}, \\
\label{eqn_s2_MLE}
s^2_{\MLE} 
&= 
\frac{1}{n}
\vy^T 
\left[ \mCInv_\vtheta - 
\frac{ \mCInv_\vtheta \vone \vone^T \mCInv_\vtheta }{\vone^T\mCInv_\vtheta \vone}
\right] \vy, \\
\nonumber
\hsigma_{\full}^2 
& = \frac{1}{n-1}
\vy^T\left[ \mC_\vtheta^{-1} 
- \frac{ \mC_\vtheta^{-1} \vone\vone^T \mC_\vtheta^{-1}}{\vone^T \mC_\vtheta^{-1} \vone}  \right]\vy
\\ 
\label{eqn:sigma2_full}
& \qquad \qquad \times  \left[\frac{(1 - \vc_{\vtheta}^T \mC_\vtheta^{-1} \vone)^2}{\vone^T \mC_\vtheta^{-1} \vone} + (c_{0\vtheta}  -\vc_{\vtheta} ^T \mC_\vtheta^{-1} \vc_{\vtheta}) \right], \\
\nonumber
 s^2_{\textup{GCV}} & = \vy^T \left[\mC_\vtheta^{-2} - \frac{\mC_\vtheta^{-2} \vone \vone^T \mC_\vtheta^{-2}}{\vone^T \mC_\vtheta^{-2} \vone}  \right] \vy  \left[ \trace(\mC_\vtheta^{-1}) \right]^{-1}, \\
\label{eqn:thetaMLE}
\vtheta_\MLE
&= \argmin_{\vtheta} \biggl \{
\log\left(\vy^T 
\left[ \mC_\vtheta^{-1} - 
\frac{ \mCInv_\vtheta \vone \vone^T \mCInv_\vtheta }{\vone^T\mCInv_\vtheta \vone}
\right] \vy 
\right)  
 +  \frac{1}{n} \log(\det(\mC_\vtheta))
\biggr \}, \\
\label{vthetaGCV}
\vtheta_{\GCV} &= \argmin_\vtheta \biggl\{\log \left(  \vy^T \left[\mC^{-2}_\vtheta - \frac{\mC^{-2}_\vtheta \vone \vone^T \mC^{-2}_\vtheta}{\vone^T \mC^{-2}_\vtheta \vone}  \right] \vy \right)  
 - \log \left ( \trace(\mC^{-2}_\vtheta) \right ) \biggr\}, \\
\label{eqn:cubMLE}
\hmu_\MLE  &= \hmu_\full =
\left(
\frac{ (1 - \vone^T  \mCInv_\vtheta\vc_{\vtheta} )  \vone }{ \vone^T \mCInv_\vtheta \vone}   +  \vc_{\vtheta} 
\right)^T  \mCInv_\vtheta \vy, \\
\label{eqn:muCV}
\hmu_{\GCV}
& = \left(\frac{(1 - \vone^T  \mC_\vtheta^{-1}\vc_{\vtheta}) \mC_\vtheta^{-1} \vone}{\vone^T \mC_\vtheta^{-2} \vone} + \vc_{\vtheta} \right)^T \mC_\vtheta^{-1} \vy.
\intertext{The credible intervals widths, $\err_{\textup{CI}}$, are given by}
\label{eqn:err_MLEGCV}
\err_{\mathsf{x}} & = 2.58 s_{\mathsf{x}} \sqrt{c_{0\vtheta} - \vc_{\vtheta}^T\mC_\vtheta^{-1}\vc_{\vtheta} }, \qquad \mathsf{x} \in \{\MLE, \GCV\},  \\ 
\err_{\textup{full}} 
& = t_{n-1,0.995} \hsigma_{\textup{full}} > \err_\MLE. \label{FJH:eq:errFull}
\end{align}
The resulting credible intervals are then
\begin{align}
\label{eqn_prob_CI}
\mathbb{P}_f \left[
|\mu-\hmu_{\mathsf{x}}| \leq \err_{\mathsf{x}} \right]  = 99\%, \qquad \mathsf{x} \in \{\MLE, \full, \GCV\}.
\end{align}
Here $t_{n-1,0.995}$ denotes the $99.5$ percentile of a standard Student's $t$-distribution with $n-1$ degrees of freedom.  In the formulas above, $\vtheta$ is assumed to take on the values $\vtheta_{\MLE}$ or $\vtheta_{\GCV}$ as appropriate.
\end{theorem}

@@

Let $\mA = \mC^{-1}_\vtheta$, let $\vzeta = \mA (\vy - m \vone)$, and partition $\mC_\vtheta$, $\mA$, and $\vzeta$ as
\begin{equation*}
\mC_\vtheta = \begin{pmatrix} c_{ii}  & \vC_{-i,i}^T \\  \vC_{-i,i} & \mC_{-i,-i}\end{pmatrix}, \qquad
\mA = \begin{pmatrix} a_{ii}  & \vA_{-i,i}^T \\  \vA_{-i,i} & \mA_{-i,-i}\end{pmatrix}, \qquad \vzeta = \begin{pmatrix} \zeta_i   \\  \vzeta_{-i} \end{pmatrix},
\end{equation*}
where the subscript $i$ denotes the $i^{\text{th}}$ row or column, and the subscript $-i$ denotes all rows or columns except the $i^{\text{th}}$. Following this notation, Lemma \ref{thrm:condDist} implies that 
\begin{align*}
\mathring{y}_i & = m + \vC^T_{-i,i} \mC_{-i,-i}^{-1} (\vy_{-i} -m \vone)  \\
\zeta_i  & = a_{ii}(y_i - m) + \vA_{-i,i}^T(\vy_{-i} - m \vone) \\
& = a_{ii}[(y_i - m) - \vC^T_{-i,i} \mC_{-i,-i}^{-1} (\vy_{-i} -m \vone)] \\
& = a_{ii}(y_i - \mathring{y}_i).
\end{align*}
Thus, \eqref{FJH:eq:CVA} may be re-written as 
\begin{align*} %\label{FJH:eq:CVB}
\textup{CV} = \sum_{i=1}^n \left(\frac{\zeta_i}{a_{ii}} \right)^2, \qquad \vzeta = \mC^{-1}_\vtheta(\vy - m \vone).
\end{align*}
The \emph{generalized cross-validation} criterion (GCV) replaces the $i^{\text{th}}$ diagonal element of $\mA$ in the denominator by the average diagonal element of $\mA$ \cite{CraWah79a,GolHeaWah79a,Wah90}:
\begin{align*} 
\textup{GCV} &
= \frac{\sum_{i=1}^n\zeta_i^2}{\left(\frac 1n \sum_{i=1}^n a_{ii} \right)^2} \\
& = \frac{(\vy - m\vone)^T \mC^{-2}_\vtheta (\vy - m \vone)}{\left(\frac 1n \trace(\mC_\vtheta^{-1}) \right)^2}.
\end{align*}

@@

The generic automatic Bayesian cubature algorithm described in the previous section requires $\Order\bigl(n \$(f) +  N_{\opt} [n^2 \$(C_\vtheta) + n^3]\bigr)$ operations to compute the cubature. Now we explain how to speed up the calculations. A key is to choose covariance kernels that match the nodes, $\{\vx_i\}_{i=1}^n$, so that the vector-matrix operations required by Bayesian cubature can be accomplished using fast Bayesian transforms at a computational cost of $\Order\bigl(n \$(f) + N_{\opt} [n \$(C_\vtheta)  + n \log(n)] \bigr)$.

@@

We have implemented the fast adaptive Bayesian cubature algorithm in MATLAB as part of the Guaranteed Adaptive Integration Library (GAIL) \cite{ChoEtal17b} as  \code{cubBayesLattice\_g}. This algorithm uses the covariance kernel defined in \eqref{eqn:ourkernel} with  $r=1$ and $2$, and the periodizing variable transforms in  \secref{period_var_tx}.  The rank-1 lattice node generator is taken from \cite{Nuy17a}  (\code{exod2\_base2\_m20}).

@@

We have developed a fast, automatic Bayesian cubature that estimates a multidimensional definite integral within a user defined error tolerance.  The stopping criteria arise from assuming the integrand to be an instance of a Gaussian process. There are three approaches:  empirical Bayes, full Bayes, and generalized cross-validation.  The computational cost of the automatic Bayesian cubature can be dramatically reduced if the covariance kernel matches the nodes.  One such match in practice is rank-1 lattice nodes and shift-invariant kernels.  The matrix-vector multiplications can be accomplished using the fast Fourier Transform.  The performance of our automatic Bayesian cubature is illustrated using three integration problems.
